It’s COMPAS-licated -- Can We Find Fairness in the COMPAS Risk Assessment Algorithm?

### 2022-03-07 Paper_Draft1/Draft1.Rmd
adding more URLs to bib
note = {\url{}}

---
title: It’s COMPAS-licated Can We Find Fairness in the COMPAS Risk Assessment Algorithm?
author:
  - name: Amrita Acharya
    affil: 1, 2
  - name: Dianne Caravela
    affil: 1, 3
  - name: Eunice Kim
    affil: 1, 4
  - name: Emma Kornberg
    affil: 1, 5
  - name: Elisabeth Nesmith
    affil: 1, 6
affiliation:
  - num: 1
    address: |
      Statistical and Data Sciences
      Smith College
      Northampton, MA 01063
  - num: 2
    email: aacharya@smith.edu
  - num: 3
    email: dcaravela@smith.edu
  - num: 4
    email: ekim89@smith.edu
  - num: 5
    email: ekornberg@smith.edu
  - num: 6
    email: enesmith@smith.edu

@@

@angwin2016machine
@bao2021s
@barocas2017fairness
@baumer2017texts
@equivant_response_2018
@gebru2021datasheets
@hardin2015data
@james2013introduction
@knight2020automated
@kypraiou_what_2021
@larson2016technical
@larson2016we
@noauthor_ai_nodate
@noauthor_aif360datasetscompasdataset_2018
@noauthor_trusted-ai_360
@noauthor_propublicacompas-analysis_2022
@noauthor_womenthetable_nodate
@vartan_1st_2022

>>>>

---
title: It’s COMPAS-licated -- Can We Find Fairness in the COMPAS Risk Assessment Algorithm?
author:
  - name: Amrita Acharya
    affil: 1, 2
  - name: Dianne Caravela
    affil: 1, 3
  - name: Eunice Kim
    affil: 1, 4
  - name: Emma Kornberg
    affil: 1, 5
  - name: Elisabeth Nesmith
    affil: 1, 6
affiliation:
  - num: 1
    address: |
      Statistical and Data Sciences
      Smith College
      Northampton, MA 01063
  - num: 2
    email: aacharya@smith.edu
  - num: 3
    email: dcaravela@smith.edu
  - num: 4
    email: ekim89@smith.edu
  - num: 5
    email: ekornberg@smith.edu
  - num: 6
    email: enesmith@smith.edu

@@
